Lattices of acyclic pipe dreams

### 2023-06-10 acyclicFacets/draft/latticePipeDreams.tex
typo
Adding a drawn picture in the proof (request of Cesar).

For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northeast of $(c_1,d_1)$.
The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$, since the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$ must have an elbow northwest of $(c_1,d_1)$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
For the crossing of $i$ and $j_m$,
the pipe $i$ has an elbow at $(a,b)$ southeast of the crossing since $a\le c_1$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northeast of the crossing.
\cref{lem:notDominant} implies that $\omega$ is not dominant and conclude the proof.
\end{proof}

Applying our \cref{thm:pipeDreamQuotient}, using the Isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.

>>>>

\centerline{\includegraphics[scale=.3]{TwoCasesofproof.pdf}}

For $c_1<a_m$, similarly to above,  we must now have $b_m<d_1$ and the pipe $j_m$ cannot have an elbow northwest of $(c_1,d_1)$.
The pipes $i<j_m$ must cross in some column strictly between $c_1$ and $a_m$, since the pipe $j_m$ must remain strictly south of $d_1$ in columns $<c_1$, but the pipe $i$ must have an elbow northwest of $(c_1,d_1)$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northwest of $i$.
For the crossing of $i$ and $j_m$,
the pipe $i$ has an elbow at $(a,b)$ southeast of the crossing since $a\le c_1$ and the pipe $j_m$ has an elbow at $(a_m,b_m)$ northeast of the crossing.
\cref{lem:notDominant} implies that $\omega$ is not dominant and conclude the proof.
\end{proof}

Applying our \cref{thm:pipeDreamQuotient}, using the isomorphism $[0e,0\omega_\nu]\cong [e,\omega_\nu]$, we get the following consequence.
